Bourke, R. H. and R. P. Garrett  Sea ice thickness distributions in the  Arctic {\it Cold Regions Science and Technology}, {\bf13}, 259-280, 1987.Chapman, W. L. and J. E. Walsh  Long range prediction of regional sea   ice anomalies in the Arctic  {\it Weather and Forecasting},  {\bf6}, 271-288, 1991.Coon, M. D., G. A. Maykut, R. S. Pritchard, D. A. Rothrock, A. S. Thorndike  Modeling the Pack Ice as an elastic-plastic material  {\it AIDJEX Bull.},  {\bf24}, 1-105, 1974.Grenfell, T. C. and G. A. Maykut  The optical properties of ice and   snow in the Arctic basin {\it J. Glaciol.}, {\bf18}, 445-469, 1977.Hibler, W. D. III and J. E. Walsh  On modeling seasonal and interannual  fluctuations of Arctic sea ice  {\it J. Phys. Oceanogr.},   {\bf12}, 1514-1523, 1982.Johnson, C. M., P. Lemke, and T. P. Barnett  Linear prediction of sea   ice anomalies. {\it J. Geophys. Res.}, {\bf90}, 5665-5675, 1985.Marsden, R. F., L. A. Mysak, and R. A. Myers  Evidence for stability   enhancement of sea ice in the Greenland and Labrador Seas    {\it J. Geophys. Res.}, {\bf96}, 4783-4789, 1991.Maykut, G. A.  The surface heat and mass balance, in The Geophysics of   Sea Ice, N. Untersteiner, ed., Plenum, NY, pp. 395-463, 1986.Maykut, G. A.  Energy exchange over young sea ice in the central Arctic  {\it J. Geophys. Res.}, {\bf83}, 3646-3658, 1978.Maykut, G. A. and P. E. Church  Radiation climate of Barrow, Alaska, 1962-66  {\it J. Appl. Met.}, {\bf12}, 620-628, 1973.Maykut, G. A. and N. Untersteiner  Some results from a time-dependent   thermodynamic model of sea ice  {\it J. Geophys. Res.}, {\bf76}, 1550-1575, 1971Parkinson, C. L. and W. M. Washington  A large scale numerical model  of sea ice  {\it J. Geophys. Res.}, {\bf84}, 311-337, 1979.Semtner, A. Jr.  A model for the thermodynamic growth of sea ice in   numerical investigations of climate  {\it J. Phys. Oceanogr.}  {\bf16}, 379-389, 1976.Thorndike, A. S., D. A. Rothrock, G. A. Maykut, and R. Colony  The thicknessdistribution of sea ice.  {\it J. Geophys. Res.}, {\bf80}, 4501-4513, 1975.Wadhams, P. M. A. Lange, and S. F. Ackley  The ice thickness distributionacross the Atlantic sector of the Antarctic ocean in midwinter.  {\it J. Geophys. Res.}, {\bf92}, 14,535-14,552, 1987.Walsh, J. E.  Empirical orthogonal functions and the statistical   predictability of sea ice extent  in Sea ice processes and models    R. S. Pritchard, ed.  pp. 373-384, 1981.Walsh, J. E. and C. M. Johnson  Interannual variability and associated   fluctuations in arctic sea ice extent  {\it J. Geophys. Res.},  {\bf84}, 6915-6928, 1979.